---
title: "Week 04 - Data Wrangling II"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
## Packages
library(learnr)
library(learnrhash)
library(tidyverse)
gradethis::gradethis_setup()

## Data
data(parlgov_election.rda)
data(parlgov_party.rda)
```

## Introduction

This week we have talked about data wrangling. 

Insert a bit more of intro prose here.

### Packages

For the following exercises, you'll need the **tidyverse** package. You should already have this packages installed, so you load it as usual by running the code below:

```{r load-packages, exercise=TRUE}
library(tidyverse)
```

## Data

The data for this exercise comes from [Parlgov](http://www.parlgov.org/), a database on parliaments and governments for all countries in the European Union.

The two data sets `parlgov_election` and `parlgov_party`, which are already loaded into the environment, contain the following variables:

- `parlgov_election`

| Variable name |  Description
|:--------------|:--------------------------------
| `country` | Abbreviated country name
| `party` | Party name
| `2014` | Vote share in the 2014 European Parliament elections
| `2019` | Vote share in the 2019 European Parliament elections

- `parlgov_party`

| Variable name |  Description
|:--------------|:--------------------------------
| `country` | Abbreviated country name
| `party` | Party name
| `family_name` | Party family
| `left_right` | Time-invariant party position on left-right scale

## Exercises

### Election results

Take a peek at the election data by running the code in the box below.

```{r glimpse-data, exercise = TRUE}
head(parlgov_election)
```
```{r question-wide-long, echo=FALSE}
question("Is this data set wide or long?",
         answer("Wide", correct = TRUE),
         answer("Long", message = "What characterizes long data? What characterizes wide data? If you need help, refer to Wickham/Grolemund (2017) Chapter 12 or the lecture material."),
         allow_retry = TRUE
         )
```

### Pivoting

Often, we need to pivot data from a wider into a longer form.

```{r question-pivot, echo=FALSE}
question_checkbox("Why? Check all possible reasons that apply.",
                  answer("Data in a wider format is not tidy.", correct = TRUE),
                  answer("A longer format is required to visualize the data.", correct = TRUE),
                  answer("Some wrong answer here"),
                  answer("Another wrong answer here"),
                  allow_retry = TRUE,
                  random_answer_order = TRUE
                  )

```

Pivot `parlgov_election` into a longer, tidy form. Name the two new resulting variables `election_year` and `vote_share`.

```{r exercise-pivot, exercise=TRUE}
parlgov_election_longer <- ___ %>%
  ___(___ = ___, 
      ___ = ___,
      ___ = ___)
```

```{r exercise-pivot-hint-1}
parlgov_election_longer <- ___ %>%
  pivot____(___ = ___,
            ___ = ___,
            ___ = ___)
```

```{r exercise-pivot-hint-2}
parlgov_election_longer <- ___ %>%
  pivot_longer(___ = ___,
               ___ = ___,
               ___ = ___)
```

```{r exercise-pivot-hint-3}
parlgov_election_longer <- ___ %>%
  pivot_longer(cols = ___, 
               names_to = ___,
               values_to = ___)
```

### Joining data sets

Next, we want to add information on the party family and left-right position from `parlgov_party` to all parties contained in `parlgov_election_longer`.

```{r question-join, echo=FALSE}
question("Which of the following joins do you need to use?",
         answer("left_join()", correct = TRUE),
         answer("right_join()", message = "right_join() would add the vote shares to the data set containing party family and left-right position - not the other way around. For more information check Wickham/Grolemund (2017) Chapter 13 or the lecture material."),
         answer("full_join()", message = "full_join() would keep all observations in both data sets. For more information check Wickham/Grolemund (2017) Chapter 13 or the lecture material."),
         answer("anti_join()", message = "anti_join() would only keep observations that do not have a match in the other data set. For more information check Wickham/Grolemund (2017) Chapter 13 or the lecture material."),
         allow_retry = TRUE,
         random_answer_order = TRUE
         )
```

Now, join both data sets as described above.

```{r prepare-join, include=FALSE}
parlgov_election_longer <- pivot_longer(parlgov_election,
                                        cols = `2014`:`2019`,
                                        names_to = "election_year",
                                        values_to = "vote_share")
```

```{r exercise-join, exercise=TRUE, exercise.setup="prepare-join"}
parlgov_joined <- ___(___, ___, ___)
```

```{r exercise-join-hint-1}
parlgov_joined <- ___(___, ___, by = ___)
```

```{r exercise-join-hint-2}
parlgov_joined <- ___(___, ___, by = c(___, ___))
```

## Submit

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(default_ui(url = "https://someurl.com"))
```
