---
title: "Week 07 - Data Visualization"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
## Packages
library(learnr)
library(learnrhash)
library(tidyverse)
gradethis::gradethis_setup()
data(data-learnr07-ep-elections.rda)
data(ep_elections)
```

**Comment GR: Data is preloaded as `ep_elections`**

## Introduction

This week we have talked about data visualization. 

Insert a bit more of intro prose here.

## Data

The data for this week is called `ep_elections` and is already already loaded into the environment. It contains information on voter turnout and total votes cast in elections for the European Parliament. You will use this data to visualise some information and gain a few more insights into the data.

Below you find an overview of the data set.

| Variable name |  Description
|:--------------|:-------------
| `country` | Country name
| `election_type` | Type of election
| `year` | Year of election
| `voter_turnout` | Voter turnout in %
| `total_vote` | Total number of voters who have turned out


### First look at the data

You can take a peek at the data using the `glimpse()` function in the box below.

```{r glimpse-data, exercise = TRUE}
glimpse(ep_elections)
```



## Exercises

### Visualizing covariation

```{r question-covariation, echo=FALSE}
question("Which of the following plots is suited to present the covariation of a categorical and a continuous variable?",
  answer("Boxplot", correct = TRUE),
  answer("Barplot", message = "A barplot is usually used to present the variation of a single categorical variable. If you need help, check Wickham/Grolemund (2017) Chapter 7 or the lecture material."),
  answer("Scatterplot", message = "A scatterplot is usually used to present the covariation of two continuous variables. If you need help, check Wickham/Grolemund (2017) Chapter 7 or the lecture material."),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

### Geometric objects

```{r question-geoms, echo=FALSE}
question("What is the function of the geometric object in ggplot2's syntax?",
  answer("It determines the type of figure.", correct = TRUE),
  answer("It specifies the length of the x- and y-axis.", message = "The length of the axes, also called limits, is specified using \"xlim()\" and \"ylim()\". This is something that we have not covered yet. If you want to learn more about this check the ggplot2 reference on how to set scale limits."),
  answer("It creates an empty coordinate system.", message = "The empty coordinate system is created by the \"ggplot()\" function. If you need help, check Wickham/Grolemund (2017) Chapter 3 or the lecture material."),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

### Jitterplots

```{r question-geom-jitter, echo=FALSE}
question("What kind of figure does \"geom_jitter()\" create?",
  answer("It creates a scatterplot, in which the observations vary slightly around their actual value.", correct = TRUE),
  answer("It creates a line plot.", message = "A line plot is created with \"geom_line()\". If you need help, check Wickham/Grolemund (2017) Chapter 3 or the lecture material."),
  answer("It adds a regression line to a figure.", message = "A regression line is added with \"geom_smooth()\". If you need help, check Wickham/Grolemund (2017) Chapter 3 or the lecture material."),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

### Faceting

```{r question-facet-grid, echo=FALSE}
question("What does the \"facet_grid()\" function do?",
  answer("It allows you to visualize subsets of data in a grid based on the values of a categorical variable.", correct = TRUE),
  answer("It adds a grid to your figure.", message = "The grid is an element of the theme. Check the lecture material for an overview of ggplot2's built-in themes or \"help(theme)\" to learn more about how to customize the grid in your figure."),
  answer("It allows you to create a grid of different types of figures.", message = "Check out the \"patchwork\" package to learn how to combine separate ggplots in one figure."),
  allow_retry = TRUE,
  random_answer_order = TRUE
  )
```

### Legends

```{r question-lineplot, echo=FALSE}
question("You want to create a lineplot. Each line is supposed to correspond to a certain value in a categorical variable in your data set. You specify \"color = categorical_variable\" but you have 50 different values in your categorical variable and the legend becomes extremely large. How do you hide the legend from the figure?",
  answer("You add \"+ theme(legend.position = \"none\")\" to your ggplot2 syntax.", correct = TRUE),
  answer("You add \"+ theme(legend.title = element_blank())\" to your ggplot2 syntax.", message = "This will only remove the title of the legend, not the legend itself. If you need help, check the lab material."),
  answer("You add \"+ theme(legend.title = \"none\")\" to your ggplot2 syntax.", message = "\"none\" is not a valid value for the argument \"legend.title\" and will therefore result in an error. If you need help, check the lab material."),
  allow_retry = TRUE,
  random_answer_order = TRUE
  )
```

### European Parliament elections

Let's turn to the data set for this learnr exercise: `ep_elections`. In the lab session, we have learned some commands for visualising data. Throughout the next set of questions, you will apply some of the things we have learned in class. 



Create a scatterplot of the variables *total_vote* and *voter_turnout*.

```{r exercise-scatterplot, exercise=TRUE}

```

<div id="exercise-scatterplot-hint">
**Hint:** Have you (correctly) specified the data and the mappings? The geometric object for creating a scatterplot is `geom_point()`.
</div>

```{r question-scatterplot, echo=FALSE}
question("What's the relationship between the two variables?",
         answer("A positive relationship", correct = TRUE),
         answer("A negative relationship", message = "A negative relationship exists when one variable increases, the other variable decreases."),
         answer("No relationship", message = "No clear relationship exists when there is no visible correlation between the two variables."),
         allow_retry = TRUE
         )
```

### Voter turnout in Germany and Austria

Next, create a boxplot and compare the 50th percentile of *voter_turnout* in Germany and Austria. 

```{r exercise-boxplot-1, exercise=TRUE}

```

<div id="exercise-boxplot-1-hint">
**Hint:** Use `filter()` to select Germany and Austria. The geometric object for creating a boxplot is `geom_boxplot()`.
</div>

```{r question-boxplot-1, echo=FALSE}
question("Is the 50th percentile in Germany...?",
         answer("higher than in Austria", correct = TRUE),
         answer("lower than in Austria", message = "Have a look at your plot again. The 50th percentile is represented by the thick line within the box."),
         answer("the same as in Austria", message = "Have a look at your plot again. The 50th percentile is represented by the thick line within the box."))
```

### Voter turnout in the entire EU

Create a boxplot for *voter_turnout* in all countries in the data set. Add a horizontal line at 60%.

```{r exercise-boxplot-2, exercise=TRUE}

```

<div id="exercise-boxplot-2-hint">
**Hint:** The geometric object for creating boxplots is `geom_boxplot()`. With `geom_hline(yintercept = 60)` you can create a horizontal line at 60%.
</div>

```{r question-boxplot-2, echo=FALSE}
question_text("How many countries have a median voter turnout higher than 60%?",
         answer("5", correct = TRUE),
         incorrect = "Are you sure you only counted the countries for which the median is higher than 60%?"
         )
```

## Submit

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(default_ui(url = "https://someurl.com"))
```
